DOpElib: Differential Equations\\ and Optimization Environment

### 2013-01-10 Examples/PDE/StatPDE/Example11/content.tex
Forgot at last checking

\subsubsection{Adding hp-Elements}
One sees by comparing  the \texttt{main.cc}-file of this problem with the one of subsection~\ref{PDE_Stat_Stokes} that the change to hp-Elements is really easy. TODO: continue, erklaere insbesondere indexsetter.

>>>>

\subsubsection{Adding hp-Elements}
One sees by comparing  the \texttt{main.cc}-file of this problem with the one of subsection~\ref{PDE_Stat_Stokes} that the change to hp-Elements is really easy, so we will keep the description short.

The obvious things to change are some templa
